Figures to insert in text

### 2018-02-27 Chapters/sdm-applications.tex
Some test to TTT boards

>>>>

\begin{forest}
  TTT/.style args={#1:#2}{
    make tab/.expanded=\forestove{content},
    label={\pgfkeysvalueof{/forest/label position #1}:$#2$}
  },
  TTT*/.style={
    make tab=::/::/::,
    content/.expand once=%
    \expandafter\vphantom\expandafter{\romannumeral-`0\forestov{content}},
    draw=none,
    append after command={(\tikzlastnode.north) edge (\tikzlastnode.south)},
    for descendants={before computing xy={l*=1.2}},
  },
  th/.style=thick,
  for tree={node options=draw, inner sep=+0pt, parent anchor=south, child anchor=north}
%
[::/::/::, TTT=r:1
  [x::/::/::, TTT=r:-1
    [x::/::/::, TTT=r:-1
      [x::/::/::, TTT=r:-1
      ]
    ]
  ]
]
\end{forest}
